Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an Empirical Study of Strategies in the Moran process for the Iterated Prisoner's Dilemma

### 2018-07-17 main.tex
Add extra comment about training criteria.
I'm not convinced it actually adds much but I think it's a
straightforward thing to add.

To carry out this numerical experiment, 164
strategies, listed (with their properties) in the Appendix,
are used from the Axelrod library. There are
43 stochastic and
121 deterministic strategies. Their memory depth,
defined by the number of rounds of history used by the strategy each round, is
shown in Table~\ref{tbl:memory_depth_count}. The memory depth is infinite if the
strategy uses the entire history of play (whatever its length). For example, a
strategy that utilizes a handshaking mechanism where the opponent's actions on
the first few rounds of play determines the strategies subsequent behavior would
have infinite memory depth.

@@

While TF1 and TF2 are competent invaders, the best invaders
in the study do not appear to employ strict handshakes, and are generally
cooperative strategies. TF3, which does not use a handshake, is a better invader
than TF1 and TF2 but not as good a resistor. Nevertheless it was the result
of the same kind of training processes and is a better combined invader-resistor
than the invaders that were trained previously to maximize payout.

>>>>

To carry out this numerical experiment, 164
strategies, listed (with their properties) in the Appendix,
are used from the Axelrod library. The appendix includes citations to the
original description of each strategy. There are
43 stochastic and
121 deterministic strategies. Their memory depth,
defined by the number of rounds of history used by the strategy each round, is
shown in Table~\ref{tbl:memory_depth_count}. The memory depth is infinite if the
strategy uses the entire history of play (whatever its length). For example, a
strategy that utilizes a handshaking mechanism where the opponent's actions on
the first few rounds of play determines the strategies subsequent behavior would
have infinite memory depth.

@@

While TF1 and TF2 are competent invaders, the best invaders
in the study do not appear to employ strict handshakes, and are generally
cooperative strategies. TF3, which does not use a handshake, is a better invader
than TF1 and TF2 but not as good a resistor. Nevertheless it was the result
of the same kind of training processes and is a better combined invader-resistor
than the invaders that were trained previously to maximize payout. It is of
interest to note that when trained in a payoff maximising criteria the finite
state machines do not evolve to obtain a handshake, this highlights the
importance of the evolutionary effect on this important mechanism.
